Popularity, Mixed Matchings, and Self-duality

### 2017-04-04 CO750-ApproximationAlgorithmsTopics/assignments/assignment_03.tex
drafted A3

where $P$ is the shortest $M$-exposing path in $H$. The second inequality follows since $M$-exposing paths are of odd length in $H$, and so $|P| \geq 5$.

@@

To complete the proof we show there are no $M$-exposing paths of length at most $3$. An $M$-exposing path of length $1$ would be a blocking pair against $M$, so by stability such a path does not exist. So suppose for a contradiction that there is an $M$-exposing path of length $3$. Say the path is $a_1b_1, b_1a_2,a_2b_2$ where $a_1b_1,a_2b_2 \in M^*$ and $b_1a_2 \in M$. Since $M^*$ is stable $a_1 \geq_{b_1} a_2$ or $b_2 >_{a_2} b_1$.

>>>>

where $P$ is the shortest $M$-augmenting path in $H$. The second inequality follows since $M$-augmenting paths are of odd length in $H$, and so $|P| \geq 5$.

@@

To complete the proof we show there are no $M$-augmenting paths of length at most $3$. An $M$-augmenting path of length $1$ would be a blocking pair against $M$, so by stability such a path does not exist. So suppose for a contradiction that there is an $M$-augmenting path of length $3$. Say the path is $a_1b_1, b_1a_2,a_2b_2$ where $a_1b_1,a_2b_2 \in M^*$ and $b_1a_2 \in M$ (with $a_1,a_2 \in A$ and $b_1,b_2 \in B$). Since $M^*$ is stable $a_1 \geq_{b_1} a_2$ or $b_2 >_{a_2} b_1$.
If $b_2 >_{a_2} b_1$ then $a_2b_2$ blocks $M$, since $b_2$ is unmatched in $M$ and prefers to be matched. Similarly if $a_1 >_{b_1} a_2$ then $a_1b_1$ blocks $M$. So $a_1 =_{b_1} a_2$, and $b_1 >_{a_2} b_2$. We claim that $a_2$ proposes to $b_1$ at most once during $\cA$. Once a woman becomes matched in $\cA$ she never becomes unmatched. Thus since $b_2$ is unmatched at the end of $\cA$ and $b_2$ is acceptable to $a_2$, $a_2$ never ran through his whole proposal list during $\cA$. Therefore $a_2$ is accepted by $b_1$ in their first proposal round. Since we know women never free partners for someone worse during $\cA$ whoever $b_1$ is paired with at any stage of the algorithm she likes at most as much as $a_1$ and $a_2$. Since $b_1$ would reject $a_2$ otherwise, this implies that $b_1$ is matched to $a_2$ during the first stage of the algorithm, and in particular during $a_1$'s first proposal. Since $a_1$ is unmatched at the end of $\cA$, we know $a_1$ proposed to $b_1$ twice, and she rejected him twice. But during the second round $a_1$ became a bachelor such that $a_1 =_{b_1} a_2$, and so $\cA$ would match $a_1b_1$ during $a_1$'s second proposal to $b_1$. But this is a contradiction. Therefore $M$-augmenting paths of length at most three do not exist.
